HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-03-18 paper/main.tex
edits
HMEANT comparison section reduced and edited

First of all, the annotation process is different. We semantically annotate the
source, then automatically project it to the translation, and ask bilingual
annotators to assess whether this projection shows a good or bad translation. In
HMEANT, they semantically annotate both the reference and the translation, then
align these manually, and assess to what extent they match.

@@

We conducted an analysis of the English UCCA Wikipedia
corpus, comprising
of 5324 sentences,
in order to assess their frequency: \begin{inparadesc}
\item[Copula clauses] are treated in HMEANT simply as instances of the main verb ``be'', which
generally does not convey the meaning of these clauses. They appear in 21.7\% of the sentences,
according to conservative estimates that only considers non-auxilliary instances of ``be''.
\item[Nominative argument structures,] which are completely ignored under HMEANT are in fact highly
pervasive, appearing in 48.7\% of the sentences.
\item[Linkers] expressing an inter-relation between
clauses (mainly discourse markers and coordinating conjunctions) appear in 56\% of the
sentences\footnote{Argument structures and linkers are explicitly marked in UCCA. We identified non-auxilliary instances of ``be'' and nouns using the NLTK standard tagger. Nominative argument structures are here defined as Scenes whose main relation is headed by a noun.}.
\end{inparadesc}

It is also relatively common in translation that verbal constructions get
nominalized or vice versa. An example from our dataset:
  ``Two {\bf review} authors assessed the studies independently\dots{}'' --
  ``Zwei Autoren bewertete die Studien unabh\"angig zu {\bf
  \"uberpr\"ufen}\dots{}'' (lit. ``Two authors assessed the studies
  independently to review\dots").\XXX{This is Omri's example, with
  Ondrej's gloss for German. Ondrej is
  not totally sure that the meaning is well preserved. So Ondrej would actually
  *remove* this example, because it would illustrate HMEANT's problems only if
  the meaning was correct.}

Another example where a linker is omitted in translation:
the source \equo{However, this review\dots}, which was translated as \equo{Diese
\"Uberpr\"ufung\dots} (lit. \equo{This review}).
This omission will not be taken into account by HMEANT at all.

We are not aware of any empirical evaluation that demonstrates that verb argument structure,
taken alone, captures the crux of the sentence semantics meanings.
The coverage of
these and other phenomena by HUME will allow to empirically determine 
(rather than stipulate), which semantic structures are important
to preserve for MT evaluation, and which are less important.

@@

HUME uses just one structural annotation (for the source) while HMEANT relies on
two independently constructed structural annotations (for both the reference and
the candidate translation).
We see this difference as crucial where semantic analysis is concerned, as it
is often impossible to assign a semantic structure to a low quality MT output sentence.

A design principle of HMEANT states that
if the translation cannot be annotated with verbal argument structure
(for whatever reason, including incomprehensibility), it cannot convey the meaning,
while HUME does not share this theoretical commitment.
For instance, consider the sentence ``a coronary angioplasty may not be technically possible'',
and the translation ``eine koronare Angioplastie kann nicht technisch m{\"o}glich''
(lit. ``a coronary angioplasty can not technically possible''),
produced by an MT system in our experiments.
The translation is correct, except that the main verb ``sein'' (``be'') is omitted.
While this may be interpreted as a minor error, HMEANT will assign the
sentence a very low score, as it failed to translate the main verb.

@@

This requires us to employ bilingual annotators, but has the benefit of avoiding
the reference translation. It is known that the reference translations are not
always literal enough and the MT output semantics can be composed differently
than the semantics of the reference. While HUME avoids this problem,
imposing a structure only on the source does prevent any fine-grained semantic
analysis of the translation.

Perhaps more importantly, references are often not created by translating the source
sentences. In some cases, the manual translation was actually carried out in the
other direction, from ``reference'' to ``source''
and in others the ``source'' and ``reference'' are independent translations
from a third language. ``References'' can thus easily contain information
that does not appear in the ``source''.

\paragraph{Annotation of Predicates Themselves}

HUME allows to annotate multi-word and even
non-contiguous elements as a single unit. HMEANT, on the other hand, always
required exactly one word to be annotated as the predicate (``Action''), which
is often linguistically inadequate.

Another problem with HMEANT identified by \perscite{bojar:wu:ssst:2012} was the
inability to indicate that the predicate is somewhat mistranslated (e.g.
accidentally negated or in a slightly wrong tense). HMEANT
annotation allows either to mark the source and reference frames as matching
(which implies that the corresponding predicates are correct translations of each
other), or as non-matching (which leads to a zero score for the whole frame) but
nothing in between. In HUME, the verb is still present as a sub-unit of the
frame and has the traffic-lights annotation.

>>>>

@@

This focus on verbal predicates has a number of unfortunate consequences. We show an example below:

\begin{center}
\begin{tabular}{lp{5.4cm}}
Source & \small a coronary angioplasty may not be technically possible \\
Transl.& \small eine koronare Angioplastie kann nicht technisch m{\"o}glich \\
Gloss & \small a coronary angioplasty can not technically possible \\
\end{tabular}
\end{center}

The German machine translation 
is largely correct, except that the main verb ``sein'' (``be'') is omitted.
While this may be interpreted as a minor error, HMEANT will assign the
sentence a very low score, as it failed to translate the main verb.

There are however a number of other serious consequences on focussing on verbal
predicates. We conducted an analysis of the English UCCA Wikipedia
corpus, comprising
of 5324 sentences,
in order to assess the impact of the following problems: 
\\
\begin{inparadesc}
\item[Copula clauses] are treated in HMEANT simply as instances of the main verb ``be'', which
generally does not convey the meaning of these clauses. They appear in 21.7\% of the sentences,
according to conservative estimates that only considers non-auxilliary instances of ``be''.
\\
\item[Nominative argument structures,] which are completely ignored under HMEANT are in fact highly
pervasive, appearing in 48.7\% of the sentences.
\\
\item[Linkers] expressing an inter-relation between
clauses (mainly discourse markers and coordinating conjunctions) appear in 56\% of the
sentences\footnote{Argument structures and linkers are explicitly marked in UCCA. We identified non-auxilliary instances of ``be'' and nouns using the NLTK standard tagger. Nominative argument structures are here defined as Scenes whose main relation is headed by a noun.}.
\end{inparadesc}

% No space
%It is also relatively common in translation that verbal constructions get
%nominalized or vice versa. An example from our dataset:
%  ``Two {\bf review} authors assessed the studies independently\dots{}'' --
%  ``Zwei Autoren bewertete die Studien unabh\"angig zu {\bf
%  \"uberpr\"ufen}\dots{}'' (lit. ``Two authors assessed the studies
%  independently to review\dots").\XXX{This is Omri's example, with
%  Ondrej's gloss for German. Ondrej is
%  not totally sure that the meaning is well preserved. So Ondrej would actually
%  *remove* this example, because it would illustrate HMEANT's problems only if
%  the meaning was correct.}

%Another example where a linker is omitted in translation:
%the source \equo{However, this review\dots}, which was translated as \equo{Diese
%\"Uberpr\"ufung\dots} (lit. \equo{This review}).
%This omission will not be taken into account by HMEANT at all.

We are not aware of any empirical evaluation that demonstrates that verb argument structure,
taken alone, captures the crux of the sentence semantics meanings.
% I am not sure that this is true
%The coverage of
%these and other phenomena by HUME will allow to empirically determine 
%(rather than stipulate), which semantic structures are important
%to preserve for MT evaluation, and which are less important.

@@

HUME uses just one structural annotation (for the source) while HMEANT relies on
two independently constructed structural annotations (for both the reference and
the candidate translation)
%First of all, the annotation process is different. We semantically annotate the
%source, then automatically project it to the translation, and ask bilingual
%annotators to assess whether this projection shows a good or bad translation. In
%HMEANT, they semantically annotate both the reference and the translation, then
%align these manually, and assess to what extent they match.
%We see this difference as crucial where semantic analysis is concerned, as it
and it is often impossible to assign a semantic structure to a low quality MT output sentence.

@@

This requires us to employ bilingual annotators, but has the benefit of avoiding
the reference translation. It is known that the reference translations are not
always literal enough and the MT output semantics can be composed differently
than the semantics of the reference.

If only monolingual annotators are available, the HUME evaluation can be performed
with a reference sentence instead of with the source. 
% While HUME avoids this problem,
%imposing a structure only on the source does prevent any fine-grained semantic
%analysis of the translation.

%Perhaps more importantly, references are often not created by translating the source
%sentences. In some cases, the manual translation was actually carried out in the
%other direction, from ``reference'' to ``source''
%and in others the ``source'' and ``reference'' are independent translations
%from a third language. ``References'' can thus easily contain information
%that does not appear in the ``source''.

\paragraph{Localisation of the Error}

In HMEANT there are no guidelines as to when to propagate and error. In HUME errors are localised as far as possible to where they occur, by the separation of atomic and structural nodes. This allows us to calculate more acurately the total score of the sentence.

%I see this a falling under the verbal structures point
%\paragraph{Annotation of Predicates Themselves}

%HUME allows to annotate multi-word and even
%non-contiguous elements as a single unit. HMEANT, on the other hand, always
%required exactly one word to be annotated as the predicate, which
%is often linguistically inadequate.

%Another problem with HMEANT identified by \perscite{bojar:wu:ssst:2012} was the
%inability to indicate that the predicate is somewhat mistranslated (e.g.
%accidentally negated or in a slightly wrong tense). HMEANT
%annotation allows either to mark the source and reference frames as matching
%(which implies that the corresponding predicates are correct translations of each
%other), or as non-matching (which leads to a zero score for the whole frame) but
%nothing in between. In HUME, the verb is still present as a sub-unit of the
%frame and has the traffic-lights annotation.
